### 2019-06-24 report/chapter03.Rnw
Results first draft

data.ext2 <- pb.process2(data)
@

@@

\section{Small study effects}
<<echo=FALSE, warning=FALSE>>=
p.samplesize.z  <- data.ext2 %>% filter(total1 + total2 > 15 & total1 + total2 < 300) %>% ungroup() %>% 
  mutate(std.z = abs(z), sample.size = total1 + total2) %>%
  group_by(sample.size) %>% 
  summarize(median.effect = median(std.z, na.rm = T)) %>% 
  ggplot(aes(x = sample.size, y = median.effect)) + geom_point(size = 0.8) + 
  theme_bw() + xlab("sample size") + ylab("median absolute z-score") +
  xlim(c(15, 300)) + ylim(c(0, 0.25)) +
  scale_x_continuous(limits = c(15, 300), breaks = c(15, 100, 200, 300))

p.samplesize.effect.sep <- data %>% filter(total1 + total2 > 15 & total1 + total2 < 300) %>% 
  filter(outcome.measure.new == "Risk Ratio" | 
           outcome.measure.new == "Odds Ratio" | 
           outcome.measure.new == "Mean Difference" |
           outcome.measure.new == "Std. Mean Difference") %>% 
  group_by(outcome.measure.new) %>% 
  mutate(sample.size = total1 + total2, scaled.effect = abs(scale(effect, center = T, scale = T))) %>%
  group_by(sample.size, outcome.measure.new) %>% 
  summarize(median.effect = median(scaled.effect, na.rm = T)) %>% 
  ggplot(aes(x = sample.size, y = median.effect, group = outcome.measure.new)) + geom_point(size = .5) + facet_wrap(~outcome.measure.new, scales = "free") + 
  theme_bw() + xlab("sample size") + ylab("median absolute normalized effect size") +
  xlim(c(15, 300)) +
  scale_x_continuous(limits = c(15, 300), breaks = c(15, 100, 200, 300))
@

The median $z$-score for a given sample size of a trial is shown in Figure \ref{z.samplesize}. It is clearly visible that the absolute value decreases with increasing sample size, i.e. that the effect size is becoming smaller. The trend flattens off after $\sim$ sample size = 400 (not shown). 
-- Appendix --

\begin{figure}
<<echo=FALSE, warning=FALSE>>=
plot(p.samplesize.z)
@
\caption{Median of the absolute $z$-score plotted against the total sample size.}
\label{z.samplesize}
\end{figure}

Only for illustration, the same trend is reproduced in Figure \ref{effect.samplesize.separated} with a similar method, using the original effect size measures ``Odds Ratio'', ``Risk Ratio'', ``Mean Difference'' and ``Std. Mean Difference'' (the most commonly used in the dataset). The ``normalized effect'' is the original effect size, normalized with respect to all other effect sizes of the same measure (i.e. subtraction of mean and division through standard error of the mean).

\begin{figure}
<<echo=FALSE>>=
plot(p.samplesize.effect.sep)
@
\caption{Median of the absolute value of the normalized, original effect size plotted against the total sample size.}
\label{effect.samplesize.separated}
\end{figure}

%Show absolute effect size depending on scaled time? Chunck 3

\section{Small Study Effect Tests}
<<echo=FALSE, warning=FALSE>>=
sig.level <- 0.1
meta.f <- meta.f %>% 
	mutate(egger.test = ifelse(pval.egger < sig.level, 1, 0),
				 thompson.test = ifelse(pval.thompson < sig.level, 1, 0),
				 begg.test = ifelse(pval.begg < sig.level, 1, 0),

@@

dat_text <- data.frame(
	label = paste(c(sum(meta.bin$harbord.test), sum(meta.bin$peter.test), 
									sum(meta.bin$rucker.test), sum(meta.bin$schwarzer.test)), "< 0.1,",
								round(c(mean(meta.bin$harbord.test), mean(meta.bin$peter.test), 
												mean(meta.bin$rucker.test), mean(meta.bin$schwarzer.test)),2)*100, "%"),
	test.type   = c("pval.harbord", "pval.peter", "pval.rucker", "pval.schwarzer"))

labels <- c(pval.harbord = "Harbord", pval.peter = "Peter", pval.rucker = "Rucker", pval.schwarzer = "Schwarzer")

p.dist.bin <- meta.bin %>% ungroup() %>% 
	select(pval.harbord, pval.peter, pval.rucker, pval.schwarzer) %>% 
	gather(key = "test.type", value = "p.value") %>% 
	ggplot(aes(x = p.value)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
	geom_text(data = dat_text, mapping = aes(x = 0.5, y = 300, label = label), color = "black") + 
	theme(strip.text.x = element_text(size=10))
#--------------------------------------------------------------------------------------------------------------------#

#Survival Outcomes:
test.cont <- meta.cont %>% ungroup() %>% summarize(egger.test = mean(egger.test),
																									 begg.test = mean(begg.test),
																									 thompson.test = mean(thompson.test))

@@

dat_text <- data.frame(
	label = paste(c(sum(meta.cont$begg.test), sum(meta.cont$egger.test), sum(meta.cont$thompson.test)), "< 0.1,",
								round(c(mean(meta.cont$begg.test), mean(meta.cont$egger.test), mean(meta.cont$thompson.test)),2)*100, "%"),
	test.type   = c("pval.begg", "pval.egger", "pval.thompson"))

labels <- c(pval.begg = "Begg Mazumdar", pval.egger = "Egger", pval.thompson = "Thompson Sharp")
p.dist.cont <- meta.cont %>% ungroup() %>% 
	select(pval.egger, pval.thompson, pval.begg) %>% 
	gather(key = "test.type", value = "p.value") %>% 
	ggplot(aes(x = p.value)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + 
	facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
	geom_text(data = dat_text, mapping = aes(x = 0.5, y = 90, label = label),  color = "black") + 
	theme(strip.text.x = element_text(size=10))
#--------------------------------------------------------------------------------------------------------------------#

@@

dat_text <- data.frame(
	label = paste(c(sum(meta.surv$begg.test), sum(meta.surv$egger.test), sum(meta.surv$thompson.test)), 
	              "< 0.1,",
								round(c(mean(meta.surv$begg.test), mean(meta.surv$egger.test), mean(meta.surv$thompson.test)),2)*100, 
								"%"),
	test.type   = c("pval.begg", "pval.egger", "pval.thompson"))

labels <- c(pval.begg = "Begg Mazumdar", pval.egger = "Egger", pval.thompson = "Thompson Sharp")
p.dist.surv <- meta.surv %>% ungroup() %>% 
	select(pval.egger, pval.thompson, pval.begg) %>% 
	gather(key = "test.type", value = "p.value") %>% 
	ggplot(aes(x = p.value)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + 
	facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
	geom_text(data = dat_text, mapping = aes(x = 0.5, y = 11, label = label),  color = "black") + 
	theme(strip.text.x = element_text(size=10))
#--------------------------------------------------------------------------------------------------------------------#

@@

agree.surv <- meta.surv %>% mutate(n.sig = egger.test + thompson.test + begg.test) %>% 
	group_by(n.sig) %>% count %>% filter(n.sig > 0) %>% 
	ggplot(aes(y = nn, x = n.sig)) + theme_bw() + geom_col() + 
  xlab("Number of significant tests") + ylab("count") + ggtitle("Continuous Outcomes")
#--------------------------------------------------------------------------------------------------------------------#
@

The results of the test for small study effects for the meta-analyses fullfilling the criteria from chapter \ref{chapter01}, section \ref{sec:Processing}, are presented in Figures \ref{fig:test.bin}, \ref{fig:test.cont} and \ref{fig:test.surv}. The histogram of the $p$-values appears most often skewed to the right, indicating evidence for small study effects. Because different tests are applied depending on outcome type, the results are displayed separately for binary, continuous and survival outcome types (as previously defined in the dataset variable ``outcome.type'', see chapter \ref{ch:chapter01}, section \ref{sec:Processing}. \\
For continuous and survival outcomes, the names refer to:

@@

\begin{figure}[!ht]
<<echo=FALSE>>=
plot(p.dist.bin)
@
\caption{Histogram of the $p$-values for small study effect in binary outcome meta-analyses. The testing method is indicated in the header, binwidth is equal to 0.1. The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
\label{fig:test.bin}
\end{figure}

\begin{figure}
<<echo=FALSE>>=
plot(p.dist.cont)
@
\caption{Histogram of the $p$-values for the small study effect in continuous outcome meta-analyses. The testing method is indicated in the header, binwidth is equal to 0.1. The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
\label{fig:test.cont}
\end{figure}

\begin{figure}
<<echo=FALSE>>=
plot(p.dist.surv)
@
\caption{Histogram of the $p$-values for the small study effect in survival outcome meta-analyses. The testing method is indicated in the header, binwidth is equal to 0.1. The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
\label{fig:test.surv}
\end{figure}

\section{Small Study Effects Adjustment}
When adjusting for small study effects, the newly obtained test statistics, as well as the corrected effect size is of interest. The former is displayed in Figures \ref{fig:adjustment.z} for the adjusted $z$-scores, \ref{fig:adjustment.smd} for the adjusted Hedges $g$ and Cohen's $d$ and \ref{fig:adjustment.log.hazard.ratio} for the adjusted log hazard ratios.

>>>>

# data.ext2 <- pb.process2(data)
@

@@

\section{Small Study Effect and Excess of Singificance Tests}
<<echo=FALSE, warning=FALSE>>=
sig.level <- 0.1
meta.f <- meta.f %>% 
	mutate(egger.test = ifelse(pval.egger < sig.level, 1, 0),
				 thompson.test = ifelse(pval.thompson < sig.level, 1, 0),
				 begg.test = ifelse(pval.begg < sig.level, 1, 0),

				 tes.d.test = ifelse(pval.d.tes < sig.level, 1, 0),

@@

dat_text <- data.frame(
  label = paste(c(sum(meta.bin$harbord.test), sum(meta.bin$peter.test), 
                  sum(meta.bin$rucker.test), sum(meta.bin$schwarzer.test), sum(meta.bin$tes.d.test, na.rm = T)), "< 0.1,",
                round(c(mean(meta.bin$harbord.test), mean(meta.bin$peter.test), 
                        mean(meta.bin$rucker.test), mean(meta.bin$schwarzer.test), mean(meta.bin$tes.d.test, na.rm = T)),2)*100, "%"),
  test.type   = c("pval.harbord", "pval.peter", "pval.rucker", "pval.schwarzer", "pval.d.tes"))

labels <- c(pval.harbord = "Harbord", pval.peter = "Peter", pval.rucker = "Rucker", pval.schwarzer = "Schwarzer", pval.d.tes = "Excess Significance")

p.dist.bin <- meta.bin %>% ungroup() %>% 
  select(pval.harbord, pval.peter, pval.rucker, pval.schwarzer, pval.d.tes) %>% 
  gather(key = "test.type", value = "p.value") %>% 
  ggplot(aes(x = p.value)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 250, label = label), color = "black") + 
  theme(strip.text.x = element_text(size=7)) + ggtitle("Binary Outcomes")
#--------------------------------------------------------------------------------------------------------------------#

#Continuous Outcomes:
test.cont <- meta.cont %>% ungroup() %>% summarize(egger.test = mean(egger.test),
																									 begg.test = mean(begg.test),
																									 thompson.test = mean(thompson.test))

@@

dat_text <- data.frame(
  label = paste(c(sum(meta.cont$begg.test), sum(meta.cont$egger.test), sum(meta.cont$thompson.test), sum(meta.cont$tes.d.test, na.rm = T)), "< 0.1,",
                round(c(mean(meta.cont$begg.test), mean(meta.cont$egger.test), mean(meta.cont$thompson.test), mean(meta.cont$tes.d.test, na.rm = T)),2)*100, "%"),
  test.type   = c("pval.begg", "pval.egger", "pval.thompson", "pval.d.tes"))

labels <- c(pval.begg = "Begg Mazumdar", pval.egger = "Egger", pval.thompson = "Thompson Sharp", pval.d.tes = "Excess significance")
p.dist.cont <- meta.cont %>% ungroup() %>% 
  select(pval.egger, pval.thompson, pval.begg, pval.d.tes) %>% 
  gather(key = "test.type", value = "p.value") %>% 
  ggplot(aes(x = p.value)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + 
  facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
  geom_text(data = dat_text, mapping = aes(x = 0.5, y = 60, label = label),  color = "black") + 
  theme(strip.text.x = element_text(size=7)) + ggtitle("Continuous Outcomes")
#--------------------------------------------------------------------------------------------------------------------#

@@

dat_text <- data.frame(
  label = paste(c(sum(meta.surv$begg.test), sum(meta.surv$egger.test), sum(meta.surv$thompson.test), sum(meta.surv$tes.d.test, na.rm = T)), "< 0.1,",
                round(c(mean(meta.surv$begg.test), mean(meta.surv$egger.test), mean(meta.surv$thompson.test), mean(meta.surv$tes.d.test, na.rm = T)),2)*100, "%"),
  test.type   = c("pval.begg", "pval.egger", "pval.thompson", "pval.d.tes"))
p.dist.surv <- meta.surv %>% ungroup() %>% 
	select(pval.egger, pval.thompson, pval.begg, pval.d.tes) %>% 
	gather(key = "test.type", value = "p.value") %>% 
	ggplot(aes(x = p.value)) + geom_histogram(boundary = 0, binwidth = 0.1) + theme_bw() + 
	facet_wrap(~test.type, labeller = labeller(test.type = labels)) + 
	geom_text(data = dat_text, mapping = aes(x = 0.5, y = 10, label = label),  color = "black") + 
	theme(strip.text.x = element_text(size=7)) + ggtitle("Survival Outcomes")
#--------------------------------------------------------------------------------------------------------------------#

@@

agree.surv <- meta.surv %>% mutate(n.sig = egger.test + thompson.test + begg.test) %>% 
	group_by(n.sig) %>% count %>% filter(n.sig > 0) %>% 
	ggplot(aes(y = nn, x = n.sig)) + theme_bw() + geom_col() + 
  xlab("Number of significant tests") + ylab("count") + ggtitle("Continuous Outcomes")
#--------------------------------------------------------------------------------------------------------------------#

################################################################################################
################################################################################################
#PUBLICATION BIAS TEST AGREEMENT
################################################################################################
################################################################################################

#Agreement proportions of publication bias tests:

#Binary:
meta.bin <- meta.bin %>%ungroup() %>%  mutate(tes.d.schwarzer = ifelse(tes.d.test == schwarzer.test, "agree", "disagree"),
																							tes.d.peter = ifelse(tes.d.test == peter.test, "agree", "disagree"),
																							tes.d.rucker = ifelse(tes.d.test == rucker.test, "agree", "disagree"),
																							tes.d.harbord = ifelse(tes.d.test == harbord.test, "agree", "disagree"),
																							schwarzer.peter = ifelse(schwarzer.test == peter.test, "agree", "disagree"),
																							schwarzer.rucker = ifelse(schwarzer.test == rucker.test, "agree", "disagree"),
																							schwarzer.harbord = ifelse(schwarzer.test == harbord.test, "agree", "disagree"),
																							rucker.peter = ifelse(rucker.test == peter.test, "agree", "disagree"),
																							rucker.harbord = ifelse(rucker.test == harbord.test, "agree", "disagree"),
																							harbord.peter = ifelse(harbord.test == peter.test, "agree", "disagree"))
agreement.bin <- meta.bin %>% ungroup() %>% summarise(tes.d.schwarzer = sum(tes.d.schwarzer == "agree")/n(),
																											tes.d.peter = sum(tes.d.peter == "agree")/n(),
																											tes.d.rucker = sum(tes.d.rucker == "agree")/n(),
																											tes.d.harbord = sum(tes.d.harbord == "agree")/n(),
																											schwarzer.peter = sum(schwarzer.peter == "agree")/n(),
																											schwarzer.rucker = sum(schwarzer.rucker == "agree")/n(),
																											schwarzer.harbord = sum(schwarzer.harbord == "agree")/n(),
																											rucker.peter = sum(rucker.peter == "agree")/n(),
																											harbord.peter = sum(harbord.peter == "agree")/n())
correlation.bin <- meta.bin %>%ungroup() %>%  summarise(tes.d.schwarzer = cor(pval.d.tes, pval.schwarzer),
																												tes.d.peter = cor(pval.d.tes, pval.peter),
																												tes.d.rucker = cor(pval.d.tes, pval.rucker),
																												tes.d.harbord = cor(pval.d.tes, pval.harbord),
																												schwarzer.peter = cor(pval.schwarzer, pval.peter),
																												schwarzer.rucker = cor(pval.schwarzer, pval.rucker),
																												schwarzer.harbord = cor(pval.schwarzer, pval.harbord),
																												rucker.peter = cor(pval.rucker, pval.peter),
																												harbord.peter = cor(pval.harbord, pval.peter))
rsquared.bin <- meta.bin %>%ungroup() %>%  summarise(tes.d.schwarzer = summary(lm(pval.d.tes~ pval.schwarzer))$r.squared,
                                                        tes.d.peter = summary(lm(pval.d.tes~ pval.peter))$r.squared,
                                                        tes.d.rucker = summary(lm(pval.d.tes~ pval.rucker))$r.squared,
                                                        tes.d.harbord = summary(lm(pval.d.tes~ pval.harbord))$r.squared,
                                                        schwarzer.peter = summary(lm(pval.schwarzer~ pval.peter))$r.squared,
                                                        schwarzer.rucker = summary(lm(pval.schwarzer~ pval.rucker))$r.squared,
                                                        schwarzer.harbord = summary(lm(pval.schwarzer~ pval.harbord))$r.squared,
                                                        rucker.peter = summary(lm(pval.rucker~ pval.peter))$r.squared,
                                                        harbord.peter = summary(lm(pval.harbord~ pval.peter))$r.squared)

binary.tests.agreement <- rbind(agreement.bin, correlation.bin, rsquared.bin)
rownames(binary.tests.agreement) <- c("Test Agreement","p-value Correlation", "p-value R-squared")
colnames(binary.tests.agreement) <- c("Excess significance, Schwarzer", "Excess significance, Peter",
                                      "Excess significance, Rucker", "Excess significance, Harbord",
                                      "Peter, Schwarzer", "Schwarzer, Rucker", "Schwarzer, Harbord",
                                      "Rucker, Peter", "Harbord, Peter")
#--------------------------------------------------------------------------------------------------------------------#

#Continuous:
meta.cont <- meta.cont %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
																								thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
																								egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
																								tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
																								thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
																								tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
agreement.cont <- meta.cont %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
																												 thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
																												 tes.d.begg = sum(tes.d.begg == "agree")/n(),
																												 thompson.egger = sum(thompson.egger == "agree")/n(),
																												 thompson.begg = sum(thompson.begg == "agree")/n(),
																												 egger.begg = sum(egger.begg == "agree")/n())
correlation.cont <- meta.cont %>% ungroup() %>% summarise(tes.d.egger = cor(pval.egger, pval.d.tes),
																													thompson.tes.d = cor(pval.thompson, pval.d.tes),
																													tes.d.begg = cor(pval.d.tes, pval.begg),
																													thompson.egger = cor(pval.thompson, pval.egger),
																													thompson.begg = cor(pval.thompson, pval.begg),
																													egger.begg = cor(pval.egger, pval.begg))
rsquared.cont <- meta.cont %>% ungroup() %>% summarise(tes.d.egger = summary(lm(pval.egger~ pval.d.tes))$r.squared,
                                                          thompson.tes.d = summary(lm(pval.thompson~ pval.d.tes))$r.squared,
                                                          tes.d.begg = summary(lm(pval.d.tes~ pval.begg))$r.squared,
                                                          thompson.egger = summary(lm(pval.thompson~ pval.egger))$r.squared,
                                                          thompson.begg = summary(lm(pval.thompson~ pval.begg))$r.squared,
                                                          egger.begg = summary(lm(pval.egger~ pval.begg))$r.squared)

cont.tests.agreement <- rbind(agreement.cont, correlation.cont, rsquared.cont)
rownames(cont.tests.agreement) <- c("Test Agreement","p-value Correlation", "p-value R-squared")
colnames(cont.tests.agreement) <- c( "Excess significance, Egger", "Excess significance, Thompson", 
                                     "Excess significance, Begg","Thompson, Egger", "Thompson, Begg", "Egger, Begg")

#--------------------------------------------------------------------------------------------------------------------#

#Survival:
meta.surv <- meta.surv %>% ungroup() %>% mutate(thompson.egger = ifelse(thompson.test == egger.test, "agree", "disagree"),
                                                thompson.begg = ifelse(thompson.test == begg.test, "agree", "disagree"),
                                                egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"),
                                                tes.d.egger = ifelse(tes.d.test == egger.test, "agree", "disagree"),
                                                thompson.tes.d = ifelse(thompson.test ==tes.d.test, "agree", "disagree"),
                                                tes.d.begg = ifelse(tes.d.test == begg.test, "agree", "disagree"))
agreement.surv <- meta.surv %>% ungroup() %>%  summarise(tes.d.egger = sum(tes.d.egger == "agree")/n(),
                                                         thompson.tes.d = sum(thompson.tes.d == "agree")/n(),
                                                         tes.d.begg = sum(tes.d.begg == "agree")/n(),
                                                         thompson.egger = sum(thompson.egger == "agree")/n(),
                                                         thompson.begg = sum(thompson.begg == "agree")/n(),
                                                         egger.begg = sum(egger.begg == "agree")/n())
correlation.surv <- meta.surv %>% ungroup() %>% summarise(tes.d.egger = cor(pval.egger, pval.d.tes),
																													thompson.tes.d = cor(pval.thompson, pval.d.tes),
																													tes.d.begg = cor(pval.d.tes, pval.begg),
																													thompson.egger = cor(pval.thompson, pval.egger),
																													thompson.begg = cor(pval.thompson, pval.begg),
																													egger.begg = cor(pval.egger, pval.begg))
rsquared.surv <- meta.surv %>% ungroup() %>% summarise(tes.d.egger = summary(lm(pval.egger~ pval.d.tes))$r.squared,
                                                          thompson.tes.d = summary(lm(pval.thompson~ pval.d.tes))$r.squared,
                                                          tes.d.begg = summary(lm(pval.d.tes~ pval.begg))$r.squared,
                                                          thompson.egger = summary(lm(pval.thompson~ pval.egger))$r.squared,
                                                          thompson.begg = summary(lm(pval.thompson~ pval.begg))$r.squared,
                                                          egger.begg = summary(lm(pval.egger~ pval.begg))$r.squared)

surv.tests.agreement <- rbind(agreement.surv, correlation.surv, rsquared.surv)
rownames(surv.tests.agreement) <- c("Test Agreement","p-value Correlation", "p-value R-squared")
colnames(surv.tests.agreement) <- c("Excess significance, Egger (survival)", "Excess significance, Thompson (survival)", 
                                    "Excess significance, Begg (survival)", "Thompson, Egger (survival)", 
                                    "Thompson, Begg (survival)", "Egger, Begg (survival)")

#--------------------------------------------------------------------------------------------------------------------#

#Merging:
test.agreement <- rbind(t(binary.tests.agreement), t(cont.tests.agreement), t(surv.tests.agreement))

#--------------------------------------------------------------------------------------------------------------------#

@

The results of the test for small study effects and excess of significance for the meta-analyses fullfilling the criteria from chapter \ref{chapter02}, section \ref{sec:Processing}, are presented in Figure \ref{fig:test}.
%Figures \ref{fig:test.bin}, \ref{fig:test.cont} and \ref{fig:test.surv}. 
The histogram of the $p$-values is displayed separately for binary, continuous and survival outcome types (as previously defined in the dataset variable \texttt{outcome.type}, see chapter \ref{ch:chapter02}, section \ref{sec:Processing}. The distributions are (with the exception of Schwarzer's test) skewed to the right, indicating evidence for small study effects. Moreover, the excess significance tests have a mode around $p = 0.4$. Large differences between small study effect tests for binary and continuous outcomes will be subject to discussion. \\
``Excess significance'' denotes the excess of significance $p$-values from the test of \citet{excess.significance}. For continuous and survival outcomes, the names refer to:

@@

\begin{figure}[ht!]
<<echo=FALSE, fig.height = 9>>=
grid.arrange(p.dist.bin,
             p.dist.cont,
             p.dist.surv, ncol = 1)
@
\caption{Histogram of the $p$-values for small study effect in meta-analyses. The testing method is indicated in the header, binwidth is equal to 0.1. The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
\label{fig:test}
\end{figure}

The agreement/coinicidence between between small study effect and excess significance tests is often not pronounced, thus, it will be compared by different methods. This is displayed in Table \ref{test.agreement}. The row names indicate which two tests are compared. First, the column ``Test Agreement'' quantifies the overall proportion by which the two tests agree in their rejection or ``acceptance'' of the null-hypothesis. ``Test Agreement'' being equal one thus indicates equivalent results, zero no correspondence whatsoever. The second column, ``Correlation'' gives the correlation between the $p$-values. A positive correlation indicates psotive coincidence of $p$-values, negative correlation coincidence in opposite directions. However, the scale might be different for this agreement measure. The ``R-squared'' value indicates to what extent one $p$-value can be predicted by another, and ignores additive differences between $p$-values (as for correlation), as well as multiplicative constants between them (i.e. $y ~ a + b*x$, $y$ and $x$ being two $p$-values of test-statistics). An R-squared value of 1 indicates perfect fit. Importantly, the order of the variables does not matter for the $p$-values for all indicators (i.e. $p$-values for $x$ and $y$ can be exchanged and the table stays the same). If a test is completely replaceable by another, all values in a row are equal to one.

<<echo=FALSE, results='asis'>>=
print(xtable(test.agreement, align = "lccc", caption = "Agreement in significance proportion, correlation and R-squared of linear regression
             between the p-values of the publication bias tests. Horizontal lines separate binary, continuous and survival outcomes (order as in table).",
             label = "test.agreement"), hline = c(0,0,9, 15, 21), size = "footnotesize")
@

\section{Small Study Effects Adjustment}
<<echo=FALSE, warning=FALSE, message=FALSE>>=
#HISTOGRAMS:

#Comparison of treatment effect p-values:
sig.zcor <- meta.f %>% mutate(z.fixef = est.z.fixef/se.est.z.fixef,
                              z.ranef = est.z.ranef/se.est.z.ranef,
                              z.reg = est.z.reg/se.est.z.reg,
                              z.copas = est.z.copas/se.est.z.copas) %>%  
  select(z.fixef, z.ranef, z.reg, z.copas) %>% gather(key = "method", value = "fisher.z") %>% 
  mutate(p.fisher.z = 2*(1-pnorm(abs(fisher.z)))) %>% 
  group_by(method) %>% 
  summarise(significant = length(which(abs(fisher.z) > 1.96)),
            p.significant = significant/length(fisher.z))
sig.zcor <- data.frame(method = sig.zcor$method,
                       label = paste(round(sig.zcor$p.significant,3)*100, "% significant", ", (n = ", sig.zcor$significant, ")", sep = ""))

method_names <- c(
  z.fixef = "Fixed Effects",
  z.ranef = "Random Effects",
  z.reg = "Regression",
  z.copas = "Copas"
)

adjustment.p.z <- meta.f %>% 
  mutate(z.fixef = est.z.fixef/se.est.z.fixef,
         z.ranef = est.z.ranef/se.est.z.ranef,
         z.reg = est.z.reg/se.est.z.reg,
         z.copas = est.z.copas/se.est.z.copas) %>%  
  select(z.fixef, z.ranef, z.reg, z.copas) %>% 
  gather(key = "method", value = "fisher.z") %>% 
  mutate(method = factor(method, levels = c("z.fixef", "z.ranef", "z.reg", "z.copas"))) %>% 
  mutate(p.fisher.z = 2*(1-pnorm(abs(fisher.z)))) %>% 
  ggplot(aes(x = p.fisher.z)) + 
  geom_histogram(boundary = 0, bins = 20) + 
  theme_bw() + 
  facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
  geom_text(data = sig.zcor, aes(x = 0.5, y = 750, label = label), position = "dodge") + 
  xlab(expression(paste(italic(p),"-value of test statistic of the ", italic(z),"-score"))) +
  ggtitle(expression(paste(italic(z), " Score ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
#--------------------------------------------------------------------------------------------------------------------#

#Comparison of SMD's:
sig.d <- meta.f %>% mutate(d.fixef = est.d.fixef/se.est.d.fixef,
                           d.ranef = est.d.ranef/se.est.d.ranef,
                           d.reg = est.d.reg/se.est.d.reg,
                           d.copas = est.d.copas/se.est.d.copas) %>%  
  select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
  mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
  group_by(method) %>% 
  summarise(significant = length(which(abs(smd) > 1.96)),
            p.significant = significant/length(smd))
sig.d <- data.frame(method = sig.d$method,
                    label = paste(round(sig.d$p.significant,3)*100, "% significant", ", (n = ", sig.d$significant, ")", sep = ""))

method_names <- c(
  d.fixef = "Fixed Effects",
  d.ranef = "Random Effects",
  d.reg = "Regression",
  d.copas = "Copas"
)

adjustment.p.d <- meta.f %>% 
  mutate(d.fixef = est.d.fixef/se.est.d.fixef,
         d.ranef = est.d.ranef/se.est.d.ranef,
         d.reg = est.d.reg/se.est.d.reg,
         d.copas = est.d.copas/se.est.d.copas) %>%  
  select(d.fixef, d.ranef, d.reg, d.copas) %>% 
  gather(key = "method", value = "smd") %>% 
  mutate(method = factor(method, levels = c("d.fixef", "d.ranef", "d.reg", "d.copas"))) %>% 
  mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
  ggplot(aes(x = p.smd)) + 
  geom_histogram(boundary = 0, bins = 20) + 
  theme_bw() + 
  facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
  geom_text(data = sig.d, aes(x = 0.5, y = 750, label = label), position = "dodge") + 
  xlab(expression(paste(italic(p),"-value of test statistic of Hedges ", italic(g)))) +
  ggtitle(expression(paste("Hedges ", italic(g), " ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
#--------------------------------------------------------------------------------------------------------------------#

#Comparison of log hazard ratios:
sig.d <- meta.f %>% filter(outcome.type == "surv") %>% 
  mutate(d.fixef = est.fixef/se.est.fixef,
         d.ranef = est.ranef/se.est.ranef,
         d.reg = est.reg/se.est.reg,
         d.copas = est.copas/se.est.copas) %>%  
  select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
  group_by(method) %>% 
  summarise(significant = length(which(abs(smd) > 1.96)),
            p.significant = (significant + sum(is.na(smd)))/(length(smd)))
sig.d <- data.frame(method = sig.d$method,
                    label = paste(round(sig.d$p.significant,3)*100, "% significant", ", (n = ", sig.d$significant, ")", sep = ""))

method_names <- c(
  d.fixef = "Fixed Effects",
  d.ranef = "Random Effects",
  d.reg = "Regression",
  d.copas = "Copas"
)

adjustment.p.log.hazard.ratio <- meta.f %>% filter(outcome.type == "surv") %>% 
  mutate(d.fixef = est.fixef/se.est.fixef,
         d.ranef = est.ranef/se.est.ranef,
         d.reg = est.reg/se.est.reg,
         d.copas = est.copas/se.est.copas) %>%  
  select(d.fixef, d.ranef, d.reg, d.copas) %>% gather(key = "method", value = "smd") %>% 
  mutate(method = factor(method, levels = c("d.fixef", "d.ranef", "d.reg", "d.copas"))) %>% 
  mutate(p.smd = 2*(1-pnorm(abs(smd)))) %>% 
  ggplot(aes(x = p.smd)) + 
  geom_histogram(boundary = 0, bins = 20) + 
  theme_bw() + 
  facet_wrap(~method, ncol = 2, labeller = as_labeller(method_names)) +
  geom_text(data = sig.d, aes(x = 0.00003, y = 20, label = label), position = "dodge") + 
  xlab(expression(paste(italic(p),"-value of test statistic of Hedges ", italic(g)))) +
  ggtitle(expression(paste("Log hazard ratio ", italic(p),"-value of Meta-Analysis and Adjustment Method")))
#--------------------------------------------------------------------------------------------------------------------#

#Meta-Analysis and adjusted treatment effect estimate difference:

#Z-score:
diff.z.fixef <- meta.f %>% 
  mutate(fixef = est.z.fixef, ranef = est.z.ranef,
                  copas = est.z.copas, regression = est.z.reg) %>% 
  mutate(copas = case_when(sign(copas) == sign(fixef) ~  abs(copas),
                           sign(copas) != sign(fixef) ~ -abs(copas)),
         regression = case_when(sign(regression) == sign(fixef) ~  abs(regression),
                                sign(regression) != sign(fixef) ~ -abs(regression)),
    fixef = abs(fixef),
    ranef = abs(ranef)) %>% 
  select(fixef, ranef, copas, regression) %>% 
  gather(key = "method", value = "adjusted.z.score", copas:regression) %>% 
  mutate(difference = fixef - adjusted.z.score) %>% 
  filter(difference > -.75 & difference < .75) %>% 
  ggplot(aes(x = difference)) + geom_histogram(binwidth = 0.1, center = 0) +
  facet_wrap(~method) + theme_bw() + 
  xlab(expression(paste("Fixed effects - adjusted ", z, "-score")))
#--------------------------------------------------------------------------------------------------------------------#
